Pteropod physiological analysis

### 2018-04-25 physio.Rmd
three explanatory variables for dissolution

library(tidyverse)
library(vegan)
library(ggord)
library(scales)
library(effects)
library(shiny)
library(plotly)
library(grid)

@@

>>>>

library(tidyverse)
library(vegan)
library(ggord)
library(scales)
library(effects)
library(shiny)
library(plotly)
library(grid)
library(MuMIn)

@@

Three explanatory variables:

```{r}
envchr <- c('Ara', 'Temp', 'O2')
ptechr <- c('dis')

dat_frm <- ptedat %>% 
  select(one_of('CTD', ptechr)) %>% 
  left_join(envdat, by = 'CTD') %>% 
  data.frame %>% 
  remove_rownames %>% 
  column_to_rownames('CTD') %>% 
  na.omit

frm <- formula(c('dis ~ (Ara + Temp + O2)^2'))
modoutglo <- lm(frm, data = dat_frm, na.action = na.pass)

modoutsel <- lm(frm, data = dat_frm, na.action = na.pass) %>% 
  dredge %>% 
  get.models(subset = 1) %>% 
  .[[1]]

summary(modoutglo)

summary(modoutsel)

```
